Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-19 paper/main.tex
First complete edit of the discussion

% previous studies
Several studies have reported increased hemodynamic activity in the PPA
attributed to the processing of spatial information, for example, when
participants were watching static pictures of landscapes compared to pictures of
faces or objects \citep[e.g.,][]{epstein1998ppa, epstein1999parahippocampal}.
% auditory semantics unclear
However, reports regarding the correlates of processing spatial information in
verbal stimulation are less clear \citep{aziz2008modulation}.
% current study: similar
In line with previous studies, we investigated the hemodynamic response to
spatial information using a model-based, mass-univariate approach.
% current study: dissimilar
However, instead of using a conventional set of stimuli, assembled to
specifically and predominantly evoke the processing of spatial information, we
employed a naturalistic movie stimulus that was designed for entertainment.

% PPA: intro
In an earlier study, \cite{bartels2004mapping} manually annotated the content of
individual movie frames (color, faces, language, and human bodies) and found
that the functional specialization of brain areas is preserved during movie
watching.
%
In contrast, we aimed to exploit a cinematographic confound in the structure of
movies, where
% establishing shots vs. e.g. over-the-shoulder shots
film directors tend to establish the spatial layout of locations in earlier
shots and later focus more on detailed depictions of people and objects
\citep{brown2012cinematography, katz1991film, mascelli1998five}.
% hypo
We hypothesized that due to the complex nature of the naturalistic stimulus,
unrelated factors would be balanced across a large number of events, and make
the bias of spatial information accessible to a convential model-based
statistical analysis of BOLD fMRI data.
% we need a detailed description -> annotation
The current model-driven approach required a detailed annotation of the
occurence of relevant stimulus features.
% event counts ftw
The annotation of both types of naturalistic stimuli, a movie and its
audio-description, revealed the respective number of incidentally occurring
events to be similar to those of a conventional experimental paradigm used to
localize functional regions of interest.

% group AV
On a group-average level, results for the audio-visual movie show significantly
increased hemodynamic activity spatially overlapping with a conventionally
localized PPA but also extending into earlier visual cortices.
% group AD
Likewise, results for the audio-description identify significant activation in
the PPA but restricted to its anterior part.
% individual level
Moroever, the group averages are representative for the majority of individual
results, where, for example, the audio-description stimulus yields bilateral
clusters in the anterior PPA of nine participants and a unilateral cluster in
one participant.
% meaning: generalization to naturalistic stimuli
These findings suggest that increased activation in the PPA during the
perception of static pictures generalizes to the perception of spatial
information embedded in a movie or a purely auditory narrative.
% narrative as substitute
The presented evidence on the in-principle suitability of a purely auditory
paradigm for localizing the PPA may offer a path to the development of
diagnostic procedures more suitable for individuals with visual impairments or
conditions like nystagmus.
% meaning: aPPA vs. pPPA
Our results provide further evidence that the PPA can be divided into functional
subregions \citep{aminoff2007parahippocampal, aminoff2015associative,
baldassano2013differential, baldassano2016two,
baumann2016functional}.\todo{claim hängt hier etwas in der Luft; wird später
ausführlicher diskutiert}

% results
Group results of the movie stimulus' primary contrast yielded a large cluster
that spans the group overlap of individual PPA ROIs from anterior to posterior.
% confound of higher perception
The cluster's extension into more posterior, earlier visual areas could be
attributed to the temporal averaging across events that did not control for
confounding visual features.
% solution
Future studies that aim to use a movie to localize visual areas in individual
participants should extensively annotate the content of frames \citep[e.g.,
using the open-source solution ``Pliers'' for feature extraction from a visual
naturalistic stimulus;][]{mcnamara2017developing}.

@@

% hypothesis
Based on the report by \cite{aziz2008modulation}, we hypothesized that semantic spatial
information embedded in the audio-description would correlate with
increased hemodynamic activity in the PPA.
% diff to Aziz (2008)
\cite{aziz2008modulation} modeled events from onset to offset of sentences,
describing unknown and famous places and faces, and compared activity levels
that were averaged across voxels of ROIs (PPA and fusiform face area, FFA
\citep{kanwisher1997ffa}) defined by a localizer experiment.
% Aziz results
Their results showed decreased activity in only the left PPA
compared to activity in the FFA for sentences describing famous places in contrast
to famous faces.
% we: model & whole brain
In the current study, we modeled events from onset to offset of single words and performed a
voxelwise whole-brain analysis.
% our results
Group results of the audio-description's primary contrast yielded significantly
increased hemodynamic activity spatially restricted to the anterior part of the
PPA group overlap.
% concluding statement
Contrary to \cite{aziz2008modulation}, our group results suggest that auditory
spatial information compared to non-spatial information correlates with
bilaterally increased activation in the anterior part of the PPA.

% previous studies: no task
It is common for conventional localizer paradigms to
employ a task to keep participants attentive to the stimuli.
% but: Epstein (1998)
Nevertheless, one early block-design study \citep{epstein1998ppa} compared
results from a paradigm that employed a perceptual judgment task of static
pictures to the same paradigm but without that task.
% results during no task
Hemodynamic activity was less but still significantly increased when
participants had no task to keep them alert and attentive to the stimuli.
% we have no task neither
The naturalistic stimulation paradigm employed here is similar in the sense that participants had no behavioral or
cognitive task \cite[e.g., forming a mental image of the stimuli;][]{ocraven2000mental} but just had to ``enjoy the presentation''.
% but still: we are different
This naturalistic paradigm nevertheless differs from \cite{epstein1998ppa},
because the relevant stimulus features were embedded in a continuous stream of complex
auditory (and visual) information which makes it unlikely that participants
speculated on the purpose of the investigation or perform undesired and unknown
evaluation or categorization of isolated stimuli.
% concluding statement: kinda automatic process
Our results therefore indicate that verbally communicated spatial information
is processed, in the anterior PPA, automatically and without specifically
guided attention.

% AD shortcomings

% optimal stimulus type in vision
In the visual domain, pictures of landscapes and not pictures of landmarks or
buildings are considered to be the ``optimal'' stimulus type
\citep{epstein2008parahippocampal}.
% we did not choose se\_new and se\_old
In the audio-description's primary contrast, we did not include the categories
that contain switches from one setting to another (\texttt{se\_new} and
\texttt{se\_old}) which one might assume to contain the auditory equivalent to
pictures of landscapes.
% why
The reason was that the categories \texttt{se\_new} and \texttt{se\_old} were
heterogeneous: they rarely contained holistic (but also vague) descriptions of
landscapes (e.g.  ``[Forrest is running through the] jungle'') but mostly
landmarks or buildings, and also non-spatial hints (e.g. ``[Jenny as a]
teenager``).
% visual system => gist in milliseconds
Humans can identify the gist of a rich visual scene within the duration of a
single fixation \citep{henderson2003human}.
%
Hence, further studies might investigate if vague verbal descriptions of
landscapes lead to a different hemodynamic activity level than descriptions of
more concrete parts of a scene (e.g.``[a] beacon'', [a] ``farmhouse'').

% AD annotation > AV annotation
Given that the annotation of nouns offered a more precise way to operationalize
the perception of spatial information than the annotation of cuts and locations,
we also hypothesized that analyzing the data from the audio-description could
localize the PPA in individual persons.
% results of dedicated localizer
The visual localizer \citep{sengupta2016extension} revealed bilateral ROIs in 12
of 14 participants and a unilateral right ROI in two participants (sub-04, sub-20).
%
Whereas \cite{sengupta2016extension} chose the subjectively ``best fitting''
$t$-threshold in a $t$-map from one of three contrasts by visual judgment, we used
the same contrast and threshold ($Z$>3.4, $p$<.05 cluster-corrected) for all
participants.
% in the current study
The audio-description yielded significant bilateral clusters in 9 of 14 participants
(of which sub-04 shows only a right-lateralized PPA ROI), and a unilateral
significant cluster in one participant.
% similar: anterior part
Similarly to the group average results, results on an individual level also
revealed that clusters are spatially restricted to the anterior part of
individual PPAs.
% conclusion
Thus, the cluster location and size found on the group level is not just a
by-product of the averaging process but a reliable pattern across results of
individual study participants.
% concluding statement
Further, our exploratory analysis suggests that a naturalistic auditory stimulus
can, in principle, be applied to localize (the anterior part) of a higher-level
visual area in the majority of participants.
% one threshold (and contrast) to rule them all
Nevertheless, further studies that aim for individual diagnostics / ROI
localization should inspect more than one contrast, and use an individual
threshold or a sphere around the local maximum \citep{poldrack2007region} in the
parahippocampal region.

% question
The fact that clusters from the auditory stimulus are spatially restricted to
the anterior part of clusters from the visual paradigms raises the question if
the revealed correlation patterns can be attributed to different features
inherent in the visual stimuli compared to the purely auditory stimulus.
% visual scenes: probably submodules
In the domain of visual scene perception, previous studies provide evidence that
the PPA can be divided into functionally subregions that might process different
stimulus features.
% posterior: functionality
The posterior PPA (pPPA) is functionally more responsive than the anterior PPA
(aPPA) to low-level features of scenes or (abstract) objects
\citep{baldassano2013differential, nasr2014thinking,
rajimehr2011parahippocampal}.
% anterior cIPL is defined using the Eickhoff–Zilles PGp probabilistic
% cytoarchitectonic map
Contrary, the aPPA is functionally more responsive than the pPPA to high-level
features of scenes (e.g. real-word size \citep{park2015parametric}; a scene's
abstract category \citep{marchette2015outside, watson2016patterns}) and
objects (e.g. spatial contextual associations \citep{aminoff2007parahippocampal, aminoff2013role}).
% connectivity
Moreover, pPPA and aPPA show differences in connectivity profiles.
% posterior
The pPPA is more strongly functionally connected to the occipital visual cortex
than the aPPA \citep{baldassano2013differential, baldassano2016two}.
% including lateral occipital cortex (LOC) and transverse occipital sulcus (TOS)
% anterior
Contrary, the aPPA is more strongly functionally connected to portions of the
default mode network, including caudal inferior parietal lobe (cIPL), the
restrosplenial complex (RSC), medial PFC and the lateral surface of the anterior
temporal lobe \citep{baldassano2013differential, baldassano2016two}.
% conclusion: subregions
According to a hypothesis by \citep{baldassano2013differential} the PPA consists
of subregions that process different aspects of a visual scene and cooperate to
build a complete scene representation.
% Their distinct connectivity properties do suggest that each may be involved in
% specific aspects of visual and cognitive processing involved in the
% overarching goal of scene understanding \citep{baldassano2013differential}.
% The fact that anterior PPA had a lower sensitivity to our abstract object
% stimuli does not necessarily imply that this region does not use object
% information \citep{baldassano2013differential}. Previous work has shown that
% PPA responds to objects that have spatial associations [Aminoff et al. 2007],
% are space-defining [Mullally and Maguire 2011], and are
% navigationally-relevant [Janzen and Van Turennout 2004]. These types of
% responses require spatial memory and cannot be based purely on visual features
% like object shape. \citep{baldassano2013differential}.  pPPA
Similarly, our results suggest that the pPPA is more concerned with visual
aspects immanent in pictures or movie shots of landscapes.
% aPPA
The aPPA might be more concerned with non-visual aspects of spatial information
(e.g. spatial contextual information \citep{aminoff2007parahippocampal}) as immanent in both visual and
verbal stimuli.

% RSC + LOC
Apart from the PPA, results show significantly increased activity in the
dorsal precuneus and posterior cingulate region (e.g. retrosplenial complex;
RSC) and lateral occipital cortex (LOC; more lateral in the movie stimulus, more
medial in the audio-description stimulus) for both naturalistic stimuli.
% RSC intro
Like the PPA, the RSC and LOC repeatedly exhibited increased hemodynamic activity
in studies investigating visual spatial perception or navigation (see
\citep{chrastil2018heterogeneity, bettencourt2013role} for reviews).
% not random shit
Thus, our model-driven approach to operationalize spatial perception based on stimulus
annotations reveals focussed activation patterns in networks that are implicated
in visual spatial perception and cognition.

% natural stimulation
In summary, natural stimuli like movies \citep{eickhoff2020towards,
hasson2008neurocinematics, sonkusare2019naturalistic} or narratives
\citep{hamilton2018revolution, honey2012not, lerner2011topographic,
silbert2014coupled, wilson2008beyond} offer an easy to implement, continuous,
complex, immersive, task-free paradigm that more closely resembles our natural
dynamic environment than traditional experimental paradigms.
% method
We took advantage of three fMRI datasets and two stimulus annotations that are
part of the studyforrest dataset
\href{http://www.studyforrest.org}{studyforrest.org} to operationalize the
perception of spatial information embedded an audio-visual movie and an auditory
narrative, and compare current results to results gained from a traditional
visual localizer.
% results
In general, results add evidence that a model-driven GLM analysis based on
annotations can be run on data from naturalistic stimuli to localize concise
functional areas and networks correlating with specific perceptual processes.
% interpretation
More specifically, our results demonstrate that increased activation in the PPA
during the perception of static pictures generalizes to the perception of
spatial information embedded in a movie and an exclusively auditory stimulus.
% interpretation: aPPA vs. pPPA
Further, our results provide evidence that the PPA can be divided into
functional subregions that coactivate during the perception of visual
scenes.
% interpretation
Lastly, a naturally engaging auditory narrative might - in principle -
substitute a visual paradigm to localize the anterior part of the PPA in
individuals with conditions that make them unable to follow task instructions
during brain scanning.

>>>>

%#1
% previous studies
Several studies have reported increased hemodynamic activity in the PPA
attributed to the processing of spatial information, for example, when
participants were watching static pictures of landscapes compared to pictures of
faces or objects \citep[e.g.,][]{epstein1998ppa, epstein1999parahippocampal}.
% auditory semantics unclear
However, reports regarding the correlates of processing spatial information in
verbal stimulation are less clear \citep{aziz2008modulation}.
% current study: similar
In line with previous studies, we investigated the hemodynamic response to
spatial information using a model-based, mass-univariate approach.
% current study: dissimilar
However, instead of using a conventional set of stimuli, assembled to
specifically and predominantly evoke the processing of spatial information, we
employed a naturalistic movie stimuli that were designed for entertainment.

%#3
% hypo
We hypothesized that due to the complex nature of a naturalistic stimulus,
unrelated factors would be balanced across a large number of events, and make
the bias of spatial information accessible to a convential model-based
statistical analysis of BOLD fMRI data.
% we need a detailed description -> annotation
This model-driven approach required a detailed annotation of the
occurence of relevant stimulus features.
% event counts ftw
The annotation of both types of naturalistic stimuli, a movie and its
audio-description, revealed the respective number of incidentally occurring
events to be similar to those of a conventional experimental paradigm used to
localize functional regions of interest.

%#4
We attempted to find hemodynamic responses to spatial information embedded in
the naturalistic stimuli, capitalizing on conceptually similar, but perceptually
different stimulation events.
% group AV
On a group-average level, results for the movie show significantly
increased hemodynamic activity spatially overlapping with a conventionally
localized PPA but also extending into earlier visual cortices.
% group AD
Likewise, results for the audio-description identify significant activation in
the PPA but restricted to its anterior part.
% individual level
Bilateral clusters in 9 of 14
participants (of which \texttt{sub-04} shows only a right-lateralized PPA ROI
in the block-design localizer results), and a unilateral
significant cluster in one participant, indicate that the group average results
are representative for the majority of individual participants.
% meaning: generalization to naturalistic stimuli
These findings suggest that increased activation in the PPA during the
perception of static pictures generalizes to the perception of spatial
information embedded in a movie or a purely auditory narrative, even though the
results may partially deviate from \cite{sengupta2016extension}, due to
the uniform cluster forming threshold employed in this study versus their
adaptive procedure (bilateral clusters in 12 of 14 participants and a unilateral
right cluster in two participants (\texttt{sub-04}, \texttt{sub-20}).

%#11 question
The fact that clusters from the auditory stimulus are spatially restricted to
the anterior part of clusters from both visual paradigms raises the question if
the revealed correlation patterns can be attributed to different features
inherent in the visual stimuli compared to a purely auditory stimulus.
% visual scenes: probably submodules
In the domain of visual scene perception, previous studies provide evidence
that the PPA can be divided into functionally subregions that might process
different stimulus features.
% posterior: functionality
The posterior PPA (pPPA) is functionally more responsive than the anterior PPA
(aPPA) to low-level features of scenes or (abstract) objects
\citep{baldassano2013differential, nasr2014thinking,
rajimehr2011parahippocampal}.
% anterior cIPL is defined using the Eickhoff–Zilles PGp probabilistic
% cytoarchitectonic map
In contrast, the aPPA responds more to high-level features of scenes (e.g.
real-word size \citep{park2015parametric}; a scene's abstract category
\citep{marchette2015outside, watson2016patterns}) and objects (e.g. spatial
contextual associations \citep{aminoff2007parahippocampal, aminoff2013role})
than the pPPA.
% connectivity
Moreover, pPPA and aPPA show differences in connectivity profiles.
% posterior
The pPPA exhibits more coactivation with the occipital visual cortex than the
aPPA \citep{baldassano2013differential, baldassano2016two}.
% including lateral occipital cortex (LOC) and transverse occipital sulcus
% (TOS) anterior
Activity in the aPPA, on the other hand, is found to be correlated with
components of the default mode network, including caudal inferior parietal lobe
(cIPL), the restrosplenial complex (RSC), medial PFC and the lateral surface of
the anterior temporal lobe \citep{baldassano2013differential,
baldassano2016two}.
% conclusion: subregions
\cite{baldassano2013differential} proposes PPA function to be the formation of
a complete scene representation, based on the processing of different aspects
of a visual scene in its subregions.
% Their distinct connectivity properties do suggest that each may be involved
% in specific aspects of visual and cognitive processing involved in the
% overarching goal of scene understanding \citep{baldassano2013differential}.
% The fact that anterior PPA had a lower sensitivity to our abstract object
% stimuli does not necessarily imply that this region does not use object
% information \citep{baldassano2013differential}. Previous work has shown that
% PPA responds to objects that have spatial associations [Aminoff et al. 2007],
% are space-defining [Mullally and Maguire 2011], and are
% navigationally-relevant [Janzen and Van Turennout 2004]. These types of
% responses require spatial memory and cannot be based purely on visual
% features like object shape. \citep{baldassano2013differential}.  pPPA
Similarly, our results suggest that the pPPA is more concerned with visual
aspects immanent in pictures or movie shots of landscapes.
% aPPA
The aPPA might be more concerned with non-visual aspects of spatial information
(e.g. spatial contextual information \citep{aminoff2007parahippocampal}) as
immanent in both visual and verbal stimuli.

%#6
% hypothesis
Based on the report by \cite{aziz2008modulation}, we hypothesized that semantic spatial
information embedded in the audio-description would correlate with
increased hemodynamic activity in the PPA. However, methods and results presented
here differ from this previous study in key aspects.
% diff to Aziz (2008)
\cite{aziz2008modulation} modeled events from onset to offset of sentences,
describing unknown and famous places and faces, and compared activity levels
that were averaged across voxels of ROIs (PPA and fusiform face area, FFA
\citep{kanwisher1997ffa}) defined by a localizer experiment.
% Aziz results
Their results showed decreased activity in only the left PPA
compared to activity in the FFA for sentences describing famous places in contrast
to famous faces.
% we: model & whole brain
Here, we modeled events from onset to offset of single words and performed a
voxelwise whole-brain analysis.
% our results
Group results of the audio-description's primary contrast yielded significantly
increased hemodynamic activity spatially restricted to the anterior part of the
PPA group overlap.
% concluding statement
Contrary to \cite{aziz2008modulation}, our results suggest that auditory
spatial information compared to non-spatial information correlates with
bilaterally increased activation in the anterior part of the PPA.

%#7
% previous studies: no task
It is common for conventional localizer paradigms to
employ a task to keep participants attentive to the stimuli.
% but: Epstein (1998)
Nevertheless, one early block-design study \citep{epstein1998ppa} compared
results from a paradigm that employed a perceptual judgment task of static
pictures to the same paradigm but without that task.
% results during no task
Hemodynamic activity was less but still significantly increased when
participants had no task to keep them alert and attentive to the stimuli.
% we have no task neither
The naturalistic stimulation paradigm employed here is similar in the sense that participants had no behavioral or
cognitive task \cite[e.g., forming a mental image of the stimuli;][]{ocraven2000mental} but just had to ``enjoy the presentation''.
% but still: we are different
This naturalistic paradigm nevertheless differs from \cite{epstein1998ppa},
because the relevant stimulus features were embedded in a continuous stream of complex
auditory (and visual) information which makes it unlikely that participants
speculated on the purpose of the investigation or perform undesired and unknown
evaluation or categorization of isolated stimuli.
% concluding statement: kinda automatic process
Our results therefore indicate that verbally communicated spatial information
is processed, in the anterior PPA, automatically and without specifically
guided attention.

% shortcomings
%#2
Our approach to stimulus annotation and event selection
differs from previous reports in the literature.
% PPA: intro
In an earlier study, \cite{bartels2004mapping} manually annotated the content of
individual movie frames (color, faces, language, and human bodies) and found
that the functional specialization of brain areas is preserved during movie
watching.
%
In contrast, we aimed to exploit a cinematographic confound in the structure of
movies, where
% establishing shots vs. e.g. over-the-shoulder shots
film directors tend to establish the spatial layout of locations in earlier
shots and later focus more on detailed depictions of people and objects
\citep{brown2012cinematography, katz1991film, mascelli1998five}.
%#8
% optimal stimulus type in vision
Moreover, in the visual domain, pictures of landscapes and not pictures of landmarks or
buildings are considered to be the ``optimal'' stimulus type
\citep{epstein2008parahippocampal}.
% we did not choose se\_new and se\_old
In the audio-description's primary contrast, we did not include the categories
that contain switches from one setting to another (\texttt{se\_new} and
\texttt{se\_old}) which one might assume to contain the auditory equivalent to
pictures of landscapes.
% why
The reason was that the categories \texttt{se\_new} and \texttt{se\_old} were
heterogeneous: they rarely contained holistic (but also vague) descriptions of
landscapes (e.g.  ``[Forrest is running through the] jungle'') but mostly
landmarks or buildings, and also non-spatial hints (e.g. ``[Jenny as a]
teenager``).
% visual system => gist in milliseconds
Humans can identify the gist of a rich visual scene within the duration of a
single fixation \citep{henderson2003human}.
%
Hence, further studies might investigate if vague verbal descriptions of
landscapes lead to a different hemodynamic activity level than descriptions of
more concrete parts of a scene (e.g.``[a] beacon'', [a] ``farmhouse'').
%#5
% results
Lastly, the group results of the movie stimulus' primary contrast yielded a large cluster
that spans the group overlap of individual PPA ROIs from anterior to posterior.
% confound of higher perception
The cluster's extent into more posterior, earlier visual areas could be
an indication that the temporal averaging across events suffered from
insufficient controlling for confounding visual features.
% solution
Future studies that aim to use a movie to localize visual areas in individual
participants should extensively annotate the content of frames \citep[e.g.,
using the open-source solution ``Pliers'' for feature extraction from a visual
naturalistic stimulus;][]{mcnamara2017developing}.

@@

%#12
% RSC + LOC
Apart from the PPA, results show significantly increased activity in the
dorsal precuneus and posterior cingulate region (e.g. retrosplenial complex;
RSC) and lateral occipital cortex (LOC; more lateral in the movie stimulus, more
medial in the audio-description stimulus) for both naturalistic stimuli.
% RSC intro
Like the PPA, the RSC and LOC repeatedly exhibited increased hemodynamic activity
in studies investigating visual spatial perception or navigation (see
\citep{chrastil2018heterogeneity, bettencourt2013role} for reviews).
% not random shit
Thus, our model-driven approach to operationalize spatial perception based on stimulus
annotations reveals focussed activation patterns in networks that are implicated
in visual spatial perception and cognition.

%#13 natural stimulation
In summary, natural stimuli like movies \citep{eickhoff2020towards,
hasson2008neurocinematics, sonkusare2019naturalistic} or narratives
\citep{hamilton2018revolution, honey2012not, lerner2011topographic,
silbert2014coupled, wilson2008beyond} can be used as a continuous, complex,
immersive, task-free paradigm that more closely resembles our natural dynamic
environment than traditional experimental paradigms.
% method
We took advantage of three fMRI datasets and two stimulus annotations that are
part of the open-data resource
\href{http://www.studyforrest.org}{studyforrest.org} to operationalize the
perception of spatial information embedded an audio-visual movie and an
auditory narrative, and compare current results to a previous report of a
conventional, block-design localizer.
% results
This report offers evidence that a model-driven GLM analysis based on
annotations can be applied to naturalistic paradigm to localize concise
functional areas and networks correlating with specific perceptual processes.
% interpretation
More specifically, our results demonstrate that increased activation in the PPA
during the perception of static pictures generalizes to the perception of
spatial information embedded in a movie and an exclusively auditory stimulus.
% interpretation: aPPA vs. pPPA
Further, our results provide evidence that the PPA can be divided into
functional subregions that coactivate during the perception of visual scenes.
% interpretation
Finally, the presented evidence on the in-principle suitability of a naturally
engaging, purely auditory paradigm for localizing the PPA may offer a path to
the development of diagnostic procedures more suitable for individuals with
visual impairments or conditions like nystagmus.

the present results suggest that a naturally engaging auditory narrative
could, in principle,
substitute a visual paradigm to localize the anterior part of the PPA in
individuals with conditions that make them unable to follow task instructions
during brain scanning.
